\documentclass[letter,margin,line]{resume}
\usepackage[defblank]{paralist}
\usepackage{multicol}
\usepackage{pdfpages}
\usepackage{anysize}
\usepackage[pdftex, unicode]{hyperref}
\hypersetup{
    pdftitle={Matthew Gambogi's Resume},
    pdfauthor={Matthew Gambogi},
    pdfborder={0 0 0},
    % Not sure if this is needed.
    unicode=true
}
\marginsize{0.5in}{1.875in}{0.6in}{0.5in}
\setdefaultitem{\footnotesize \textbullet}{}{}{}{}{}
\setdefaultleftmargin{0em}{}{}{}{}{}
\setdefaultenum{(a)}{(1)}{}{}{}{}
\newcommand{\rurl}[1]{\hfill {\footnotesize \url{#1}}}
\newcommand{\rdate}[1]{\hfill {\small #1}}
\renewcommand{\employer}[6]{\item[#1] - #2 \rdate{#3} \\* #4 \rurl{#5}\\* #6}
\newcommand{\project}[2]{\item {\bf #1}\\{\small #2}\\}
    \begin{document}
    \name{\huge Matthew Gambogi}
    \begin{resume}
        \section{\mysidestyle Contact} \vspace{2mm}

        \begin{multicols}{3}
                  (703) 999-3742 \\
                  \href{mailto:m@gambogi.com}{m@gambogi.com} \\
                  \href{http://matt.gambogi.com}{matt.gambogi.com} \\
                  \href{https://github.com/gambogi}{github.com/gambogi}

            \columnbreak
            {\bf Permanent Address} \\
                  312 Pathway Pl SW \\
                  Leesburg, VA 20175

            \columnbreak
            {\bf School Address} \\
                   704 Park Point Dr \\
                   Apt. No. 1 \\
                   Rochester, NY 14623 

        \end{multicols}
        \section{\mysidestyle Education}
        \begin{compactdesc}
        \item[Rochester Institute of Technology] - Rochester, NY
            \rdate{Spring 2017 (Expected)}
        \item B.S. Computer Science, Economics
        \end{compactdesc}

        \section{\mysidestyle Work Experience}
        \begin{asparadesc}
            \employer{Intuit}
                     {San Diego, CA}
                     {January - August 2015}
                     {Software Engineer Intern}
                     {http://turbotax.intuit.com}
                     {
                         As a member of the TurboTax Data Science team:
                         \begin{itemize}[]
                             \item Contributed to design of novel machine learning algorithm.
                             \item Created highly composable DSL for specifying data
                                   transformation pipelines. Models could be specified in Python and
                                   compiled to Java.
                                   Featured guarenteed termination by construction.
                             \item Developed and deployed coninuous integration solution for Python.
                             \item Recieved "Win Together" award for accomplishments.
                         \end{itemize}
                     }
            \employer{Janssen Pharmaceutical}
                     {Remote}
                     {Fall 2014, Fall 2015 - Present}
                     {Software Engineer Intern}
                     {http://janssen.com}
                     {Used Haskell and 4store (graph database) to analyze material 
                      flow through a pharmaceutical recipie. Part-time.}\\
            \employer{athenahealth}
                     {Boston, MA}
                     {Summer 2014}
                     {Software Engineer Intern}
                     {http://athenahealth.com}
                     {Member of the Security Development team.
                      Engineered automated cross-site scripting
                      (XSS) vulnerability detection system.
                      Specifically targeted a large Perl web application. 
                     }\\
            \employer{Kaprica Security}
                     {Reston, VA}
                     {Summer 2013}
                     {Software Engineer Intern}
                     {http://kapricasecurity.com}
                     {Developed Python web application using Flask,
                      SQLAlchemy backed by PostgreSQL.
                      Worked on frontend, backend. Also contacted suppliers
                      for potential hardware obfuscation solutions.
                     }\\
            \employer{SecureIT}
                     {Reston, VA}
                     {Summer 2012}
                     {Cyber Ninja (Research Intern)}
                     {http://secureit.com}
                     {Studied, tested, and developed exploitation and
                      exploit prevention techniques.
                      Worked on DARPA contracts. 
                      Tested on an experimental (now patented)
                      Control Flow Integrity system.
                      Investiged a potential side channel attack vector
                      in the Android keyboard process.
                     }
        \end{asparadesc}

        \section{\mysidestyle Technical Skills}
        \begin{compactdesc}
        \item[Languages] { \small
                 Python,
                 C,
                 Haskell,
                 OCaml,
                 Lisp,
                 Perl,
                 Java,
                 MIPS,
                 HTML/CSS
            }
        \item[Tools] { \small
                gdb,
                git,
                Perforce,
                OracleSQL,
                postgreSQL,
                VerticaSQL,
                vim,
                Eclipse,
                \LaTeX
            }
        \end{compactdesc}
        \section{\mysidestyle Personal Projects}
        \begin{asparablank}
            \project{CSH Evals}
            {
                Working with a small team of peers on a Haskell web application
                and API for automating large portions of the Computer Science
                House's evaluations process, member database.
            }
            \project{Typed Language Evaluator (TyLE)}
            {
                Toy simply typed lambda calculus interpreter in Haskell.
                Self-taught type theory, parser combinators.
            }
        \end{asparablank}
        \section{\mysidestyle Extracurricular}
        \begin{asparadesc}
            \employer{Computer Science House ({\small CSH})}
                     {}
                     {2012 - Present}
                     {Active Member}
                     {https://csh.rit.edu/}
                     {A 40 year old selective student technical organization,
                      emphasizing technical projects and group learning.
                      Elected History Director (Alumni Relations) 2014.
                     }
        \end{asparadesc}
    \end{resume}
    \end{document}
